Supplementary Information

### 2020-05-31 doc/manuscript/MEE_manuscript.Rmd
Update MEE_manuscript.Rmd

>>>>

```{r eval=FALSE, echo=FALSE}

# I tried to put in table, as in [Camille's paper](https://github.com/EcoClimLab/ForestGEO-tree-size-carbon/blob/master/paper_treesize_draft.Rmd), but couldn't make it work.
library(knitr)
library(kableExtra)
sites <- read.csv("tables_figures/sites.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(sites)
      #caption = "Study sites")
```
